---
title: "RAM scrap monitor"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}
options(digits=2)
library(flexdashboard)
library(plotly)
library(varhandle)
library(tidyr)
library(dplyr)
library(ggplot2)
```

General info {data-icon="fas fa-plane-departure"}
=============================

Row {data-width=150}
--------------------------------------
### Total scrap generated in all areas in Tonnes per day

```{r}

library(openxlsx)
scrap.ramheb<-read.xlsx("Dechets hebdomadaire par zone.xlsx")

data3<-scrap.ramheb
data3$Poids<-as.numeric(data3$Poids)

quant<-sum(data3$Poids)/7
valueBox(round(quant,digits=2), icon = "fa fa-recycle")


```

### Total annual scrap in Tonnes

```{r}

quant1<-sum(data3$Poids)*52
valueBox(round(quant1,2), icon = "fas fa-trash-alt",color="seagreen")
```

### Ratio of dangerous scrap in technical zone

```{r}
zonetech<-read.csv("zonetech.csv",sep=";")
data0<-zonetech

datas<-subset(data0,data0$Type_scrap=="D",c(Type_scrap,POIDS_Tonnes))
datas1<-subset(data0,data0$Type_scrap=="ND",c(Type_scrap,POIDS_Tonnes))
qtyD<-sum(datas$POIDS_Tonnes)
qtyND<-sum(datas1$POIDS_Tonnes)
ratio<-qtyD/qtyND
valueBox(round(ratio,2), icon = "fas fa-fire",color="red")
```


Column
--------------------------------------
### Time series of scrap in ZIRAM
> Below you'll find presented the time serie of scap in ZIRAM in 2018; That year was considered as the most recent year which can be judged as normal in terms of activity:
    
```{r}

scrap.ram<-read.csv("scrap.csv",sep=";")

data3<-scrap.ram
data3$Scrap.Date<-as.Date(data3$Scrap.Date,"%d/%m/%Y")

data4<-data3 %>%
        group_by(Scrap.Date) %>%
        summarise(somme=sum(Qty),na.rm=TRUE) %>%
        select(Scrap.Date,somme)
g<-ggplot(data4, aes(x = Scrap.Date, y = somme)) + 
        geom_line(color="steelblue")+xlab("Date")+ylab("Quantity of consummable scrap in technical area RAM")+ggtitle("Time serie of consummable scrap in ZIRAM in 2018")
ggplotly(g)

```

Atelier Roues/Freins {data-icon="fas fa-search"}
===========================

Row
--------------------------------------

### Search for scrap in workshop Roues/Freins

> Scrap generated in Workshop Roues/Freins

There are scrap that aren't mentionned on this dashbooard because they are generated in small amount per period like : Toboggan - Gilet de sauvetage - Vitres (2-3 per month).

Important info about this workshop: ATR tire is generated 10 times per month (destined to be thrown away)- Disques freins et patins freins aren't destined to be thrown away,some of them are reutilizable. 

```{r}
scrap_workshop<-read.xlsx("Atelier1_1.xlsx")
Tonneperyear<-c(16,0.4,0.12,0.15,0.1,1.2,0.48,4.8,4.8,3.6,2.4,2.5,4,0.6,0.26,0.3,0.05,6.5,13,0.14,0.06,0.8,0.06 ,0.25,0,0.0325,1.125,0.6,0.6,2.4,0.1,3)
scrap_workshop1<-scrap_workshop[,1:4]
scrap_workshop2<-cbind(scrap_workshop1,Tonneperyear)
scrap_workshop4<-scrap_workshop1[,1:2]
scrap_workshop5<-cbind(scrap_workshop4,Tonneperyear)

library(DT)
datatable(scrap_workshop5, options = list(pageLength =5))

```

column
--------------------------------------

### Top generated scrap annually in Workshop Roues/Freins 

```{r}
data7<-scrap_workshop5 %>%
        group_by(DESIGNATION) %>%
        summarise(somme=sum(Tonneperyear),na.rm=TRUE) %>%
        select(DESIGNATION,somme)
data6pic<-subset(data7,data7$somme>=2)
data6pic <- data6pic[order(data6pic$somme, decreasing=TRUE), ]
data6pic$cumulative <- cumsum(data6pic$somme)
data6pic$DESIGNATION <- factor(data6pic$DESIGNATION, levels=data6pic$DESIGNATION)
g<-ggplot(data6pic, aes(x=DESIGNATION)) 
g1<-g+geom_bar(aes(y=somme),fill= "blue",stat="identity") +
geom_point(aes(y=cumulative), color = rgb(0, 1, 0), pch=16, size=1) +
geom_path(aes(y=cumulative, group=1), colour="slateblue1", lty=3, size=0.9) +
theme(axis.text.x = element_text(angle=0, vjust=0.6)) +
labs(title = "Pareto Plot of top generated scrap annually in Workshop Roues/freins", subtitle = "RAM", x = 'DESIGNATION', y =
'Weights in Tonnes')
ggplotly(g1)
```   

column
--------------------------------------
### Ratio of scrap generated in Wshop1 compared to the others 

```{r}
total<-sum(as.numeric(scrap.ramheb$Poids))*52+sum(as.numeric(data7$somme))
ratio_roue<-sum(data7$somme)/total

valueBox(round(ratio_roue,2), icon = "fas fa-cogs",color="gray")
```

### Scrap generated in Wshop1 annually in Tonnes

```{r}

total<-sum(scrap_workshop5$Tonneperyear)


valueBox(round(total,digits=2), icon = "fas fa-calculator",color="orange")
```

Scrap in PISTE {data-icon="fas fa-search"}
===========================
Row
--------------------------------------
### Ratio of generated scrap in PISTE compared to the total

```{r}
scrap_piste<-subset(scrap.ramheb,Zone=="Piste")
total_piste<-sum(as.numeric(scrap_piste$Poids))
total<-sum(as.numeric(scrap.ramheb$Poids))+sum(as.numeric(data7$somme))*1/52
ratio_piste<-total_piste/total
valueBox(round(ratio_piste,digits=2), icon = "fas fa-road")
```

### Percentage of dangerous scrap in PISTE

```{r}
scrap_piste<-subset(scrap.ramheb,Zone=="Piste")
Percentage <-(1.2+0.2)/total_piste
valueBox(round(Percentage,digits=2), icon = "fas fa-fire",color="red")
```

### Total scrap generated in PISTE weekly in Tonnes

```{r}
valueBox(round(total_piste,2), icon = "fas fa-calculator",color="gray")
```

### Estimated frequence of collecting scrap in PISTE in times/weeks

```{r}
valueBox(1/2, icon = "fas fa-truck",color="green")
```

Row {data-height=150}
--------------------------------------
### Weekly scrap in Piste 

```{r}
scrap_piste <- scrap_piste[order(scrap_piste$Poids, decreasing=TRUE), ]
scrap_piste$cumulative <- cumsum(scrap_piste$Poids)
scrap_piste$Déchets <- factor(scrap_piste$Déchets, levels=scrap_piste$Déchets)
g<-ggplot(scrap_piste, aes(x=Déchets)) 
g1<-g+geom_bar(aes(y=Poids),fill= "blue",stat="identity") +
geom_point(aes(y=cumulative), color = rgb(0, 1, 0), pch=16, size=1) +
geom_path(aes(y=cumulative, group=1), colour="slateblue1", lty=3, size=0.9) +
theme(axis.text.x = element_text(angle=4, vjust=0.6)) +
labs(title = "Pareto Plot of top generated scrap weekly in Workshop Piste", subtitle = "RAM", x = 'Déchets', y =
'Weights in Tonnes')
ggplotly(g1)

```

### Search for scrap

```{r}
library(DT)
datatable(scrap_piste, options = list(pageLength =5))
```


Atelier batteries-fours-CE {data-icon="fas fa-search"}
===========================
Row
--------------------------------------
### Ratio of generated scrap in Atelier batteries. fours et chauffe-eaux compared to the total

```{r}
scrap_bat<-subset(scrap.ramheb,Zone=="Atelier batteries. fours et chauffe-eaux")
scrap_bat$Poids<-as.numeric(scrap_bat$Poids)
total_bat<-sum(as.numeric(scrap_bat$Poids))
total<-sum(as.numeric(scrap.ramheb$Poids))+sum(as.numeric(data7$somme))*1/52
ratio_bat<-total_bat/total
valueBox(round(ratio_bat,2), icon = "fas fa-car-battery")
```

### Percentage of dangerous scrap in Atelier batteries. fours et chauffe-eaux

```{r}
scrap_bat<-subset(scrap.ramheb,Zone=="Atelier batteries. fours et chauffe-eaux")
Percentage <-(0.012+0.0165+0.001+0.0210+0.002)/total_bat

valueBox(round(Percentage,2), icon = "fas fa-fire",color="red")
```

### Total scrap generated in Atelier batteries. fours et chauffe-eaux weekly in Tonnes

```{r}
valueBox(round(total_bat,2), icon = "fas fa-calculator",color="gray")
```


Row
--------------------------------------


### Weekly scrap in Atelier batteries. fours et chauffe-eaux

```{r}
scrap_bat <- scrap_bat[order(scrap_bat$Poids, decreasing=TRUE), ]
scrap_bat$cumulative <- cumsum(scrap_bat$Poids)
scrap_bat$Déchets <- factor(scrap_bat$Déchets, levels=scrap_bat$Déchets)
g<-ggplot(scrap_bat, aes(x=Déchets)) 
g1<-g+geom_bar(aes(y=Poids),fill= "blue",stat="identity") +
geom_point(aes(y=cumulative), color = rgb(0, 1, 0), pch=16, size=1) +
geom_path(aes(y=cumulative, group=1), colour="slateblue1", lty=3, size=0.9) +
theme(axis.text.x = element_text(angle=4, vjust=0.6)) +
labs(title = "Weekly scrap in Atelier batteries. fours et chauffe-eaux", subtitle = "RAM", x = 'Déchets', y =
'Weights in Tonnes')
ggplotly(g1)
```

### search for scrap

>Remarks:

There are other types of scrap that aren't mentionned on this dashboard like: Frame boiler,Water boiler and Réservoires but they represent a minority compared to the others in terms of weight per period.

```{r}
library(DT)
datatable(scrap_bat, options = list(pageLength =5))
```

Atelier Cabine {data-icon="fas fa-search"}
===========================
Row
--------------------------------------
### Ratio of generated scrap in Atelier Cabine compared to the total

```{r}
scrap_cabine<-subset(scrap.ramheb,Zone=="Atelier Cabine")
total_cabine<-sum(as.numeric(scrap_cabine$Poids))
total<-sum(as.numeric(scrap.ramheb$Poids))+sum(as.numeric(data7$somme))*1/52
ratio_cabine<-total_cabine/total
valueBox(round(ratio_cabine,2), icon = "fas fa-seat")
```

### Percentage of dangerous scrap in Atelier Cabine

```{r}
scrap_cabine<-subset(scrap.ramheb,Zone=="Atelier Cabine")
Percentage <-(0)/total_cabine
valueBox(round(Percentage,2), icon = "fas fa-fire",color="red")
```

### Total scrap generated in Atelier cabine weekly in Tonnes

```{r}
valueBox(round(total_cabine,2), icon = "fas fa-calculator",color="green")
```


Row
--------------------------------------
### Weekly scrap in Atelier Cabine

```{r}
scrap_cabine <- scrap_cabine[order(scrap_cabine$Poids, decreasing=TRUE), ]
scrap_cabine$cumulative <- cumsum(scrap_cabine$Poids)
scrap_cabine$Déchets <- factor(scrap_cabine$Déchets, levels=scrap_cabine$Déchets)
g<-ggplot(scrap_cabine, aes(x=Déchets)) 
g1<-g+geom_bar(aes(y=Poids),fill= "blue",stat="identity") +
geom_point(aes(y=cumulative), color = rgb(0, 1, 0), pch=16, size=1) +
geom_path(aes(y=cumulative, group=1), colour="slateblue1", lty=3, size=0.9) +
theme(axis.text.x = element_text(angle=4, vjust=0.6)) +
labs(title = "Weekly scrap in Atelier Cabine", subtitle = "RAM", x = 'Déchets', y =
'Weights in Tonnes')
ggplotly(g1)

```

### Search for scrap

```{r}
library(DT)
datatable(scrap_cabine, options = list(pageLength =5))
```

Atelier Structure {data-icon="fas fa-search"}
===========================
Row
--------------------------------------
### Ratio of generated scrap in Atelier Structure compared to the total

```{r}
scrap_structure<-subset(scrap.ramheb,Zone=="Atelier structure")
total_structure<-sum(as.numeric(scrap_structure$Poids))
total<-sum(as.numeric(scrap.ramheb$Poids))+sum(as.numeric(data7$somme))*1/52
ratio_structure<-total_structure/total
valueBox(round(ratio_structure,2), icon = "fas fa-plane")
```

### Percentage of dangerous scrap in Atelier structure

```{r}

Percentage <-(1e-03+1e-04)/total_structure
valueBox(round(Percentage,2), icon = "fas fa-fire",color="red")
```

### Total scrap generated in Atelier Structure weekly in Tonnes

```{r}
valueBox(round(total_structure,2), icon = "fas fa-calculator",color="gray")
```


Row
--------------------------------------
### Weekly scrap in Atelier Structure

```{r}
scrap_structure <- scrap_structure[order(scrap_structure$Poids, decreasing=TRUE), ]
scrap_structure$cumulative <- cumsum(scrap_structure$Poids)
scrap_structure$Déchets <- factor(scrap_structure$Déchets, levels=scrap_structure$Déchets)
g<-ggplot(scrap_structure, aes(x=Déchets)) 
g1<-g+geom_bar(aes(y=Poids),fill= "blue",stat="identity") +
geom_point(aes(y=cumulative), color = rgb(0, 1, 0), pch=16, size=1) +
geom_path(aes(y=cumulative, group=1), colour="slateblue1", lty=3, size=0.9) +
theme(axis.text.x = element_text(angle=4, vjust=0.6)) +
labs(title = "Weekly scrap in Atelier Structure", subtitle = "RAM", x = 'Déchets', y =
'Weights in Tonnes')
ggplotly(g1)

```

### Search for scrap

```{r}
library(DT)
datatable(scrap_structure, options = list(pageLength =5))
```

Autres {data-icon="fas fa-search"}
===========================

> Atelier NDT:

The only type of scrap generated in this area is NDT liquid which is considered to be very dangerous.

> Atelier Magasin

 The types of scrap generated in Magasin are considered to be infinitesimal compared to the others.The majority of them are: Grease(D)-Packing(ND)-Coating(D)-Pot de peinture(D).

Forecasts {data-icon="fas fa-chart-line"}
===========================
Row 
-------------


### Forecast for the next 70 days using Neural Networks

> Forecast for the next 70 days using Neural Networks

```{r}


library(lubridate)
library(dplyr)
library(forecast)
scrap.data<-read.csv("scrap.csv",sep=";")

data3<-scrap.data
data3$Scrap.Date<-as.Date(data3$Scrap.Date,"%d/%m/%Y")

data4<-data3 %>%
        group_by(Scrap.Date) %>%
        summarise(somme=sum(Qty),na.rm=TRUE) %>%
        select(Scrap.Date,somme)

data5<-data4 %>%
        complete(Scrap.Date = seq(first(Scrap.Date), last(Scrap.Date),by="day"), 
                 fill = list(somme = 0)) 


library(forecast)
library(caret)
dat_ts = ts(data5["somme"])
fit <- nnetar(dat_ts, lambda=0.5)
fcast <- forecast(fit, PI=TRUE, h=20)
autoplot(fcast)



```

### Predicted values for the upcoming days

```{r}
library(DT)
tableau<-data.frame(fcast)
datatable(tableau, options = list(pageLength =10))
```